Resurgence of the Airy function

### 2022-06-30 airy-resurgence.tex
Switch to more convenient exponent

For each $a \in \C$, the expression $|g(a, \cdot)\,d\zeta|$ defines a {\em density} on $\Omega \smallsetminus \{a\}$---a norm on the tangent bundle which is compatible with the conformal structure. The square of a density is a Riemannian metric. Let $\ell_{g, \Omega}(a)$ be the distance from $\zeta = 0$ to $a$ with respect to the density $|g(a, \cdot)\,d\zeta|$ on $\Omega \smallsetminus \{a\}$. The bound
\begin{align*}
\big|[\mathcal{G}f](a)\big| & \le \left| \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right| \\
& \le \int_{\zeta = 0}^{a} |f|\,|g(a, \cdot)\,d\zeta| \\
& \le \|f\|_\infty \int_{\zeta = 0}^{a} |g(a, \cdot)\,d\zeta|
\end{align*}
holds for any integration path. Taking the infimum over all paths, we see that
\[ \big|[\mathcal{G}f](a)\big| \le \ell_{g, \Omega}(a)\,\|f\|_\infty. \]
so $\|\mathcal{G}\| \le \sup_{a \in \Omega} \ell_{g, \Omega}(a)$. Crucially, we can always make $\|\mathcal{G}\|$ a contraction by restricting $\Omega$.
\subsubsection{The example of fractional integrals}
Setting $g(a, a') = (\zeta(a) - \zeta(a'))^{-\nu}$ with $\nu \in (-\infty, 1)$, we get the fractional integral $\partial^{\nu-1}_{\zeta \text{ from } 0}$. The density $|\zeta(a) - \zeta|^{-\nu}\,|d\zeta|$ is rotationally symmetric around $a$, so the shortest path from $\zeta = 0$ to $a$ is a straight line with respect to $|d\zeta|$ \textcolor{magenta}{[check]}. It follows that
\begin{align*}
\ell_{g, \Omega}(a) & = \int_0^{|\zeta(a)|} t^{-\nu}\,dt \\
& = \tfrac{1}{1-\nu} |\zeta(a)|^{1-\nu},
\end{align*}
so
\[ \|\partial^{\nu-1}_{\zeta \text{ from } 0}\| \le \sup_\Omega \tfrac{1}{1-\nu} |\zeta|^{1-\nu}. \]
In particular, $\partial^{\nu-1}_{\zeta \text{ from } 0}$ is a contraction of $\holoL{\infty}(\Omega)$ whenever $\|\zeta\|_\infty < (1-\nu)^{1/(1-\nu)}$.
\subsection{Order shifting}\label{shifting}
Consider holomorphic functions on a simply connected open set that touches but doesn't contain $\zeta = 0$. A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point. We'll say a function is {\em slight} at $\zeta = 0$ if it can be written as
\begin{equation}\label{eqn:slight-defn}
\zeta^{\alpha_1} f_1 + \ldots + \zeta^{\alpha_r} f_r + g
\end{equation}
where $f_1, \ldots, f_r$ are regular, $\alpha_1, \ldots, \alpha_r \in \R \smallsetminus \Z$, and $g, g', g'', \ldots$ go to zero at $\zeta = 0$.

>>>>

For each $a \in \C$, the expression $|g(a, \cdot)\,d\zeta|$ defines a {\em density} on $\Omega \smallsetminus \{a\}$---a norm on the tangent bundle which is compatible with the conformal structure. The square of a density is a Riemannian metric. Let $\ell_{g, \Omega}(a)$ be the distance from $\zeta = 0$ to $a$ with respect to the density $|g(a, \cdot)\,d\zeta|$ on $\Omega \smallsetminus \{a\}$. The bound
\begin{align*}
\big|[\mathcal{G}f](a)\big| & \le \left| \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right| \\
& \le \int_{\zeta = 0}^{a} |f|\,|g(a, \cdot)\,d\zeta| \\
& \le \|f\|_\infty \int_{\zeta = 0}^{a} |g(a, \cdot)\,d\zeta|
\end{align*}
holds for any integration path. Taking the infimum over all paths, we see that
\[ \big|[\mathcal{G}f](a)\big| \le \ell_{g, \Omega}(a)\,\|f\|_\infty. \]
so $\|\mathcal{G}\| \le \sup_{a \in \Omega} \ell_{g, \Omega}(a)$. Crucially, we can always make $\|\mathcal{G}\|$ a contraction by restricting $\Omega$.
\subsubsection{The example of fractional integrals}
Setting $g(a, a') = (\zeta(a) - \zeta(a'))^{-\lambda-1}$ with $\lambda \in (-\infty, 0)$, we get the fractional integral $\partial^\lambda_{\zeta \text{ from } 0}$. The density $|\zeta(a) - \zeta|^{-\lambda-1}\,|d\zeta|$ is rotationally symmetric around $a$, so the shortest path from $\zeta = 0$ to $a$ is a straight line with respect to $|d\zeta|$ \textcolor{magenta}{[check]}. It follows that
\begin{align*}
\ell_{g, \Omega}(a) & = \int_0^{|\zeta(a)|} t^{-\lambda-1}\,dt \\
& = -\tfrac{1}{\lambda} |\zeta(a)|^{-\lambda},
\end{align*}
so
\[ \|\partial^\lambda_{\zeta \text{ from } 0}\| \le \sup_\Omega {(-\tfrac{1}{\lambda}) |\zeta|^{-\lambda}}. \]
In particular, when $\|\zeta\|_\infty < 1$, the operator $\partial^\lambda_{\zeta \text{ from } 0}$ is a contraction of $\holoL{\infty}(\Omega)$ for all $\lambda \in (-\infty, 0)$.
\subsection{Order shifting}\label{shifting}
Consider holomorphic functions on a simply connected open set that touches but doesn't contain $\zeta = 0$. A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point. We'll say a function is {\em slight} at $\zeta = 0$ if it can be written as
\begin{equation}\label{eqn:slight-defn}
\zeta^{\alpha_1} f_1 + \ldots + \zeta^{\alpha_r} f_r + g
\end{equation}
where $f_1, \ldots, f_r$ are regular, $\alpha_1, \ldots, \alpha_r \in \R \smallsetminus \Z$, and $g, g', g'', \ldots$ go to zero at $\zeta = 0$.
